\documentclass[10pt,letterpaper]{extarticle}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

\setstretch{1.4}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.75em}


\begin{document}
	
	\begin{center}
		{\LARGE \textbf{Nilson Aldair Molina Rengifo}}\\[4pt]
		\textbf{Backend / Full-Stack Software Developer}\\[6pt]
		\href{mailto:nilsonmolina@outlook.com}{nilsonmolina@outlook.com} • 
		\href{https://wa.me/573209030250}{(+57) 320 903 0250} • 
		\href{https://linkedin.com/in/nilsonmolina}{linkedin.com/in/nilsonmolina}
	\end{center}
	
	\vspace{1em}
	\hrule
	\vspace{1em}

	Dear Hiring Team at Cloudbeds,
	
	I'm writing to apply for the Senior Backend Engineer role within the Payments team. I'm motivated by opportunities where backend systems are not just about delivering features, but about reliability, correctness, and long-term sustainability in environments where failures have real business impact.
	
	Over the years, I've worked primarily on backend-heavy systems that operate under real production constraints: systems with active users, operational dependencies, and non-trivial failure modes. I'm comfortable taking ownership of services and features end to end, from design and implementation to deployment, monitoring, and stabilization in production. That includes making trade-offs when needed, understanding the operational cost of technical decisions, and collaborating closely with product and business stakeholders to deliver pragmatic solutions.
	
	I've spent a significant part of my experience working with PHP-based backends, relational databases, and API-driven integrations, often in systems that evolved over time and required careful refactoring rather than greenfield rewrites. I'm particularly comfortable working in environments where data consistency, observability, and system resilience matter, and where code quality is directly tied to operational stability.
	
	Beyond the technical side, I value clear communication and shared ownership. I'm used to working with distributed teams, discussing design decisions openly, contributing to reviews, and staying calm and effective when things don't behave as expected in production. I don't see engineering as an isolated activity, but as a collaboration between people with different perspectives working toward a common outcome.
	
	Cloudbeds' focus on building reliable, scalable platforms for a global audience, especially in a domain as sensitive as payments, aligns well with how I approach software engineering. I'm interested in contributing to systems where correctness, security, and thoughtful design are not optional, but fundamental.
	
	Thank you for considering my application. I would welcome the opportunity to discuss how my experience and approach could add value to the Payments team at Cloudbeds.
	
	Best regards,
	
	Nilson Aldair Molina Rengifo

\end{document}